PM Mungbean meta-analysis

### 2020-06-10 02_Preliminary_analysis.Rmd
Alter season length and first sign of disease plot to include estimated season lengths where planting dates or harvest dates were missing

@@

```{r first_incidence}
# Create the data frame for the plot
source("R/import_data.R")
PM_MB_means <- import_data()
season_dates <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      Planting_date = unique(planting_date),
      Harvest_date = unique(harvest_date),
      First_sign_PM = unique(first_sign_disease),
      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date))
   )

@@

season_dates[1:2, "Planting_day"] <- 1
#  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day

@@

# reorder the factors so they will appear in chronilogical order
# I used First sign because all trials have recorded this
season_dates$trial_ref <-
   factor(season_dates$trial_ref,
          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])

# Plot
season_dates %>%
   ggplot() +
   geom_pointrange(aes(
      x = trial_ref,
      y = Disease_day,
      ymin = Planting_day,
      ymax = Harvest_day
   )) +
   scale_y_continuous(limits = c(
      0,
      max(
         season_dates$Planting_day +
            season_dates$season_length,
         na.rm = TRUE
      )
   ),
   labels = axis_labels_date,
   breaks = first_day_month) +
   geom_point(aes(x = trial_ref, y = Disease_day)) +
   coord_flip() +
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
warnings()
```

>>>>

This tests when rainfall during the cropping season could be best associated with yield

@@

```{r first_incidence}
# Create the data frame for the plot
season_dates <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      Planting_date = unique(planting_date),
      Harvest_date = unique(harvest_date),
      First_sign_PM = unique(first_sign_disease),
      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
      cropping_season = "Actual"
   )

# For some trials where planting date and Harvest date is missing lets estimate 
#     the season length by using the mean of all season lengths
season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"

season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
   as.numeric(mean(season_dates$season_length, na.rm = TRUE))

season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
   as.numeric(mean(season_dates$season_length, na.rm = TRUE))

season_dates[is.na(season_dates$season_length),"season_length"] <- 
   mean(season_dates$season_length, na.rm = TRUE)

@@

season_dates[c(1:2,6), "Planting_day"] <- 1
#  yday(as.Date("2012-02-28") - 7) # Correct dplanted in december and emerged in February, Assuming due to lack of rain or recording error. Using 7 days prior to emergence day as planting day

@@

# reorder the factors so they will appear in chronological order
# I used First sign because all trials have recorded this
season_dates$trial_ref <-
   factor(season_dates$trial_ref,
          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])

# Plot
season_dates %>%
   ggplot() +
   geom_pointrange(aes(
      x = trial_ref,
      y = Disease_day,
      ymin = Planting_day,
      ymax = Harvest_day,
      colour = cropping_season
   )) +
   scale_y_continuous(limits = c(
      0,
      max(
         season_dates$Planting_day +
            season_dates$season_length,
         na.rm = TRUE
      )
   ),
   labels = axis_labels_date,
   breaks = first_day_month) +
   geom_point(aes(x = trial_ref, y = Disease_day)) +
   coord_flip() +
   scale_color_manual(values=c("black","grey70"))+
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")
